---
title: "Project: December 13, 2022"
output: html_notebook
---

# Modeling Goalie Save Percentages using Individual Player Attributes

```{r Library}
library(dplyr)  
library(ggplot2)  
library(stats)
library(olsrr)
library(leaps)
library(GGally)
library(lubridate)
library(stringr)
library(tidyr)
library(mosaic)
library(agricolae)
library(lmtest)
library(mctest)
library(MASS)
library(ggpubr)
```

## Project Rationale

As justification for our analysis, we create a linear model demonstrating that team point percentage increases with goalie save percentage. Teams have a strong incentive to seek out strategies to identify goalies with characteristics that could lead to a high save percentage.

```{r}
# set the working directory to pwd
setwd('.')

# read the csv file 'WinningPercentage.csv' and assign it to the variable 'teams'
teams <- read.csv('./WinningPercentage.csv', header = TRUE)

# display the first 4 rows of the dataframe 'teams'
head(teams,4)

# create a linear model with the variable 'Points' as the response variable and 'Save' as the predictor
teammodel = lm(Points~Save, data = teams)

# display a summary of the linear model
summary(teammodel)

# display the coefficients of the linear model
coef(teammodel)

# display the confidence intervals of the linear model coefficients
confint(teammodel)

# create a function that represents the line of best fit
teamfunction=function(x){4.407*x-3.449}

# create a scatter plot with 'Save' on the x-axis and 'Points' on the y-axis
# and add the line of best fit using the 'teamfunction'
ggplot(data=teams,mapping= aes(x=Save,y=Points))+
  geom_point()+
  stat_function(fun=teamfunction,geom="line")+
  ggtitle("Team Points Percentage vs. Team Save Percentage (1997/98-2018/19)")+
  labs(y= "Team Points Percentage", x = "Team Save Percentage")
```

$$
\mbox{The estimated model for Points Percentage is:}\\
\hat{PointPCT}=- 3.449 + 4.407 SAVEPCT
$$

## Main Dataset Modeling and Analysis

```{r}
goalies = read.csv("./goalies_merged.csv", header = TRUE)
head(goalies, 10)
tail(goalies,10)
```

### output of unique values for (factor)columns pre-wrangling

```{r}
unique(goalies$ShootsCatches_x)
unique(goalies$Country)
unique(goalies$Season)
length(unique(goalies$Country))
table(unlist(goalies$Country))
unique(goalies$DraftYear)
unique(goalies$DraftRound)
```

### Setting data types and data manipulation:

```{r}
goalies = subset(goalies, select = c('ShootsCatches_x','Country','HeightInches','GamesStarted','GamesPlayed_y','WeightPounds','Season','DOB','DraftYear','DraftRound','FirstSeason','SavePct','TimeOnIce','Shutouts_y','PenaltyMinutes'))

## Rookie year calculation 
RookieYear = numeric(length(goalies$FirstSeason))
for (j in 1:length(goalies$FirstSeason))
{
  RookieYear[j] = c(as.integer(strtrim(goalies$FirstSeason[j], 4)))
}

goalies$RookieYear = RookieYear


## Years in minors calculation
goalies$DraftYear = as.integer(goalies$DraftYear)
YIM = numeric(length(goalies$FirstSeason))
for (k in 1:length(goalies$FirstSeason))
{
  YIM[k] = c(goalies$RookieYear[k] - goalies$DraftYear[k])
}

goalies$YIM = YIM


## Find age 
age = numeric(length(goalies$DOB))
for (p in 1:length(goalies$DOB))
{
       age[p] = as.integer(strtrim(goalies$Season[p], 4)) - as.integer(strtrim(goalies$DOB[p], 4))
}

goalies$age = age


## Creates factor variable for DraftCategory [Round 1/2, rounds 3/4, Later Round, Undrafted]
goalies <- goalies %>%
  mutate(DraftCategory = case_when(
    (goalies$DraftRound == "--") ~ "undrafted",
    (goalies$DraftRound < 3) ~ "early",
    (goalies$DraftRound < 5) ~ "middle",
    (goalies$DraftRound > 4) ~ "late"
    ))


## TOI in minutes calculation (time on ice)
goalies <- goalies %>%
   mutate(TOI = as.integer(str_split(goalies$TimeOnIce, ":", simplify = TRUE)[ , 1]))

## Years since drafted calculation: Season - draft year 
goalies <- goalies %>%
  mutate(YSD = as.integer(strtrim(goalies$Season, 4)) -  goalies$DraftYear)

## Years in NHL calculation
goalies <- goalies %>%
  mutate(YrsNHL = as.integer(strtrim(goalies$Season, 4)) -  as.integer(goalies$FirstSeason))

## Start percentage calculation
goalies <- goalies %>%
  mutate(StartPct = goalies$GamesStarted / goalies$GamesPlayed_y)

## Country of origin factor variable creation [CAN, USA, SWE, FIN, OTHER]
for (i in 1:length(goalies$Country))
{
    if (goalies$Country[i] == "USA") {goalies$Country[i] = "USA"
    }  else if (goalies$Country[i] == "CAN") {goalies$Country[i] = "CAN"
    }  else if (goalies$Country[i] == "FIN") {goalies$Country[i] = "FIN"
    }  else if (goalies$Country[i] == "SWE") {goalies$Country[i] = "SWE"
    } else {goalies$Country[i] = "OTHER"}
}

## Era factor variable creation [1,2,3]
goalies <- goalies %>%
  mutate(Era = case_when(
    (as.integer(strtrim(goalies$Season, 4)) < 1996) ~ "4",
    (as.integer(strtrim(goalies$Season, 4)) > 1995 & as.integer(strtrim(goalies$Season, 4)) < 2004) ~ "1",
    (as.integer(strtrim(goalies$Season, 4)) > 2003 & as.integer(strtrim(goalies$Season, 4)) < 2012) ~ "2",
    (as.integer(strtrim(goalies$Season, 4)) > 2011 & as.integer(strtrim(goalies$Season, 4)) < 2019) ~ "3",
    (as.integer(strtrim(goalies$Season, 4)) > 2018) ~ "5"
    ))


## to remove: any year before 1997, 2012-2013, and greater than 2018 
goalies <- goalies[goalies$Era %in% c("1","2","3"), ]
goalies %>% drop_na()
goalies

## to turn svpct from proportion to percentage
goalies$SavePct = goalies$SavePct*100

## for reference, lockout 1994-95 (48 games played), lockout 2004-05 (0 games played), lockout 2012-13 (48 games) seasons, covid 2020-21 (56 games)
```

###output of unique values for (factor)columns and calculated columns post-wrangling

```{r}
unique(goalies$ShootsCatches_x)
unique(goalies$Country)
table(unlist(goalies$Country))
unique(goalies$Season)
unique(goalies$DraftYear)
unique(goalies$DraftRound)
unique(goalies$DraftCategory)
unique(goalies$YIM)
unique(goalies$RookieYear)
unique(goalies$Era)
unique(goalies$YSD)
unique(goalies$age)
```

###Fav stats of "wrangled" dataset:

```{r}
favstats(goalies$Ht)
favstats(goalies$Wt)
favstats(goalies$Round)
favstats(goalies$TOI)
favstats(goalies$SavePct)
colnames(goalies)

```

###we want to trim the data to remove goalies with small amounts of games played so they do no influence the model (if they were a temporary replacement, only for 1 game, etc)

```{r}
favstats(goalies$GamesPlayed_y)
favstats(goalies$GamesStarted)
```

###explore the data

```{r}
ggplot(data=goalies,aes(GamesPlayed_y,SavePct, color = Era)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)
ggplot(data=goalies,aes(GamesStarted,SavePct, color = Era)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)
ggplot(data=goalies,aes(TOI,SavePct, color = Era)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)

ggplot(data=goalies,aes(GamesPlayed_y,SavePct, color = Country)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)
ggplot(data=goalies,aes(GamesStarted,SavePct, color = Country)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)
ggplot(data=goalies,aes(TOI,SavePct, color = Country)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)

ggplot(data=goalies,aes(GamesPlayed_y,SavePct, color = DraftCategory)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)
ggplot(data=goalies,aes(GamesStarted,SavePct, color = DraftCategory)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)
ggplot(data=goalies,aes(TOI,SavePct, color = DraftCategory)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)
```

$$
\begin{aligned}
&\mbox{We can calcuate that the MEAN [GamesPlayed] = 25}\\
&\mbox{We can calculate the AVERAGE of [GamesStarted] = 26.9}\\
&\mbox{In order to be elgibable for the Vezina, a goalie must start at least 25 games}\\
&\mbox{Set our minumum [GamesPlayed] to determine NHL-starting goalies = 25 --> trim data where [GamesPlayed] > 24}\\
\end{aligned}
$$
### Trim games played to \>=25 and convert savepct to \>1 numeric value (\*100)

```{r}
## keep all rows games played 25 or more
goalies_new <- subset(goalies,GamesPlayed_y > 24 )

rownames(goalies_new) <- seq(length=nrow(goalies_new))

##check new DF
head(goalies_new, 10)
##check all unqiue values in modified column gamesplayed 
unique(goalies_new$GamesPlayed_y)
## goalies_new$SavePct = goalies_new$SavePct*100
## goalies_new
```

### Recheck plots from before

```{r}
ggplot(data=goalies_new,aes(GamesPlayed_y,SavePct, color = Era)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)
ggplot(data=goalies_new,aes(GamesStarted,SavePct, color = Era)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)
ggplot(data=goalies_new,aes(TOI,SavePct, color = Era)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)

```

$$
\begin{aligned}
H_0&: \beta_i = 0\\
H_A&: \beta_i \neq0\\
i&=predictor\  variables
\end{aligned}
$$

$$
\begin{aligned}
H_0&:\beta_1 =\beta_2 = \beta_i = 0 \\
H_a&:\mbox{at least one }\beta_i\mbox{ is not zero } \\
i&=x, y, z, ...[predictor\ variables] \\
\alpha &= 0.05  
\end{aligned}
$$

### Creating the full-model with the original DF with all data to check

```{r}
colnames(goalies)
full.goalies = lm(SavePct ~ factor(ShootsCatches_x) + HeightInches + WeightPounds + factor(Country) + factor(DraftCategory) + YSD + age + YIM + factor(Era) + StartPct + TOI + Shutouts_y + PenaltyMinutes, data = goalies)
summary(full.goalies)

```

### Re-run the model with new df with gamesplayed \>= 25

```{r}
colnames(goalies_new)
full.goalies_new = lm(SavePct ~ factor(ShootsCatches_x) + HeightInches + WeightPounds + factor(Country) + factor(DraftCategory) + YSD + age + YIM + factor(Era) + StartPct + TOI + Shutouts_y + PenaltyMinutes, data = goalies_new)
summary(full.goalies_new)

##runs to here

```

### Build best first order model based on pvalue \> 0.05 variables

```{r}
goalies.additive.only = lm(SavePct ~ factor(Era)+ Shutouts_y + PenaltyMinutes, data = goalies_new)
summary(goalies.additive.only)
```

### Equation for first order "best" model - OLD 

$$
\begin{aligned}
\widehat{SVPCT}_i&=
\begin{cases} 
89.8523+0.2634Shutouts-0.0069PenaltyMinutes & \mbox{if } i^{th}\mbox{  ERA is 1 (1996/97 - 2003/04)} \\
90.0577+0.2634Shutouts-0.0069PenaltyMinutes & \mbox{if } i^{th}\mbox{ ERA is 2 (2005/06 - 2011/12)}\\
90.6449+0.2634Shutouts-0.0069PenaltyMinutes & \mbox{if } i^{th}\mbox{ERA is 3 (2013/14 - 2018/19)}
\end{cases}
\end{aligned}
$$

###rebuild 1st order model drop p \> 0.05

```{r}
goalies.additive.only2 = lm(SavePct ~ factor(Era)+ Shutouts_y, data = goalies_new)
summary(goalies.additive.only2)
```

###equation for first order "best" model 

$$
\begin{aligned}
\widehat{SVPCT}_i&=
\begin{cases} 
89.8055+0.2601Shutouts & \mbox{if } i^{th}\mbox{  ERA is 1 (1996/97 - 2003/04)} \\
90.0798+0.2601Shutouts & \mbox{if } i^{th}\mbox{ ERA is 2 (2005/06 - 2011/12)}\\
90.1156+0.2601Shutouts & \mbox{if } i^{th}\mbox{ERA is 3 (2013/14 - 2018/19)}
\end{cases}
\end{aligned}
$$

```{r}
ggplot(data=goalies_new,aes(GamesPlayed_y,TOI, color = DraftCategory)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)
ggplot(data=goalies_new,aes(WeightPounds,HeightInches, color = Country)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)
ggplot(data=goalies_new,aes(Shutouts_y,StartPct, color = Era)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)
ggplot(data=goalies_new,aes(Shutouts_y,GamesPlayed_y, color = Country)) + geom_point(alpha=0.5, size=2)+ geom_smooth(method = "lm", se = FALSE)

```

```{r}
##colnames(goalies_new)
full.goalies_2nd = lm(SavePct ~ (factor(ShootsCatches_x) + HeightInches + WeightPounds + factor(Country) + factor(DraftCategory) + YSD + age + YIM + factor(Era) + StartPct + TOI + Shutouts_y + PenaltyMinutes)^2, data = goalies_new)
summary(full.goalies_2nd)

```

```{r}
goalies.interact = lm(SavePct ~ Shutouts_y + factor(Era) + age + StartPct + factor(Country) + factor(DraftCategory) + YIM + YSD + WeightPounds + TOI+ factor(ShootsCatches_x)+ factor(DraftCategory):factor(Era) + factor(DraftCategory):YIM + factor(Country):factor(Era) + factor(Country):factor(DraftCategory) + age:WeightPounds + YSD:WeightPounds + factor(Country):WeightPounds + factor(ShootsCatches_x):WeightPounds + TOI:Shutouts_y + StartPct:Shutouts_y, data = goalies_new)
summary(goalies.interact)
```

```{r}
goalies.interact.2 = lm(SavePct ~ Shutouts_y + factor(Era) + age + StartPct + factor(Country) + factor(DraftCategory) + YIM + YSD + WeightPounds + TOI +  factor(DraftCategory):factor(Era) + factor(DraftCategory):YIM + factor(Country):factor(Era) + factor(Country):factor(DraftCategory) + age:WeightPounds + YSD:WeightPounds + factor(Country):WeightPounds + TOI:Shutouts_y + Shutouts_y:StartPct, data = goalies_new)
summary(goalies.interact.2)
```

```{r}
goalies.interact.3 = lm(SavePct ~ Shutouts_y + factor(Era) + age + StartPct + factor(Country) + factor(DraftCategory) + YIM + YSD + WeightPounds + TOI +  factor(DraftCategory):factor(Era) + factor(DraftCategory):YIM + factor(Country):factor(Era) + factor(Country):factor(DraftCategory) + YSD:WeightPounds + factor(Country):WeightPounds + TOI:Shutouts_y + Shutouts_y:StartPct, data = goalies_new)
summary(goalies.interact.3)
```

```{r}
goalies.interact.4 = lm(SavePct ~ Shutouts_y + factor(Era) + StartPct + factor(Country) + factor(DraftCategory) + YIM + WeightPounds + TOI +  factor(DraftCategory):factor(Era) + factor(DraftCategory):YIM + factor(Country):factor(Era) + factor(Country):factor(DraftCategory) + factor(Country):WeightPounds + TOI:Shutouts_y + Shutouts_y:StartPct, data = goalies_new)
summary(goalies.interact.4)
```

```{r}
goalies.interact.5 = lm(SavePct ~ Shutouts_y + factor(Era) + factor(Country) + factor(DraftCategory) + YIM + WeightPounds + TOI +  factor(DraftCategory):factor(Era) + factor(DraftCategory):YIM + factor(Country):factor(Era) + factor(Country):factor(DraftCategory) + factor(Country):WeightPounds + TOI:Shutouts_y, data = goalies_new)
summary(goalies.interact.5)
```

```{r}
goalies.interact.final = lm(SavePct ~ Shutouts_y + factor(Era) + factor(Country) + factor(DraftCategory) + YIM + WeightPounds + TOI +  factor(DraftCategory):factor(Era) + factor(DraftCategory):YIM + factor(Country):factor(Era) + factor(Country):WeightPounds + TOI:Shutouts_y, data = goalies_new)
summary(goalies.interact.final)
```

```{r}
coefficients(goalies.interact.final)
```

### Run the VIF test on the primary terms in the interaction model

```{r}
##VIF test
goalies.maineffects = lm(SavePct ~ Shutouts_y + factor(Era) + factor(Country) + factor(DraftCategory) + YIM + WeightPounds + TOI, data = goalies_new)
imcdiag(goalies.maineffects, method = "VIF")
```

### No multicollinearity in the main predictor variables

### Test our model assumptions

```{r}
ggpairs(goalies.interact.final, lower = list(continuous = "smooth_loess", combo = "facethist", discrete = "facetbar", na = "na"))
```

### No higher-order terms - test assumptions

### Checking for conditions:

```{r}
best.model <- goalies.interact.final

###### Plot for normality 
ggplot(best.model, aes(x=.fitted, y=.resid)) + geom_point() +geom_smooth() + geom_hline(yintercept = 0)

###### Check Equal Variance Assumption by graphs and the Breusch-Pagan test. If you detect a trend, how would you like to transform the predictors in the model?
bptest(best.model)

###### Shapiro-Wilk normality test also confirms that the residuals are normally distributed if the p-value is larger than the determined alpha value
shapiro.test(residuals(best.model))

ggplot(data=best.model, aes(residuals(best.model))) + geom_histogram(breaks = seq(-5,5,by=.3), col="red", fill="blue") + labs(title="Histogram for residuals") + labs(x="residuals", y="Count")

ggplot(best.model, aes(sample=residuals(best.model))) + stat_qq() + stat_qq_line()

###### VIF test to verify there is no collinearity was completed on the main additive variables and no multicollinearity was found.



###### Looking for outliers: 
## Residuals vs Leverage plot
plot(best.model,which=5)

## Cooks Distance
plot(best.model,pch=18,col="red",which=c(4))

## cooksD <- cooks.distance(best.model)
## influencial <- cooksD[(cooksD > (4/length(goalies_new$SavePct)))]
## influencial

## Leverage Points. Must run this format with the "run chunk" button 
p = length(coef(best.model))
n = nrow(goalies_new)
lev = hatvalues(best.model)

##plot(rownames(goalies_new), lev)
##abline(h = 2 *p/n, lty = 1)
##abline(h = 3 *p/n, lty = 1)

outlier3p = lev[lev>(3*p/n)]
outlier3p

outlier2p = lev[lev>(2*p/n)]
outlier2p

```

```{r}
Outliers_3p <- c(241,242,367,368,384,385,413,414,480,529,530,531,532,533,583,675,678,679,802,803,804,805,806,807,808,809,903)
Outliers_2p <- c(61,105,240,241,242,349,351,352,354,355,362,364,366,367,368,384,385,386,387,413,414,480,485,529,530,531,532,533,549,550,551,552,555,556,557,558,559,560,561,562,582,583,615,618,619,620,671,672,673,674,675,678,679,721,726,739,740,741,742,743,744,745,746,747,772,773,774,775,776,777,778,779,780,781,802,803,804,805,806,807,808,809,813,814,857,871,872,901,902,903,904,905,906)
```

```{r}
goalies_no_outliers <- goalies_new[-Outliers_3p,]
goalies_no_outliers
```

```{r}
goalies.interact.final.no_outliers = lm(SavePct ~ Shutouts_y + factor(Era) + factor(Country) + factor(DraftCategory) + YIM + WeightPounds + TOI +  factor(DraftCategory):factor(Era) + factor(DraftCategory):YIM + factor(Country):factor(Era) + factor(Country):WeightPounds + TOI:Shutouts_y, data = goalies_no_outliers)
summary(goalies.interact.final.no_outliers)
```

```{r}
best.model <- goalies.interact.final.no_outliers

###### Plot for normality 
ggplot(best.model, aes(x=.fitted, y=.resid)) + geom_point() +geom_smooth() + geom_hline(yintercept = 0)

###### Check Equal Variance Assumption by graphs and the Breusch-Pagan test. If you detect a trend, how would you like to transform the predictors in the model?
bptest(best.model)

###### Shapiro-Wilk normality test also confirms that the residuals are normally distributed if the p-value is larger than the determined alpha value
shapiro.test(residuals(best.model))

ggplot(data=best.model, aes(residuals(best.model))) + geom_histogram(breaks = seq(-5,5,by=.3), col="red", fill="blue") + labs(title="Histogram for residuals") + labs(x="residuals", y="Count")

ggplot(best.model, aes(sample=residuals(best.model))) + stat_qq() + stat_qq_line()
```

```{r}
bc_goalies = boxcox(best.model, lambda=seq(0,20))
```

```{r}
bestlambda_goalie = bc_goalies$x[which(bc_goalies$y==max(bc_goalies$y))]
bestlambda_goalie
```

```{r}
bcmodel_goalies = lm((((SavePct^bestlambda_goalie)-1)/bestlambda_goalie) ~ Shutouts_y + factor(Era) + factor(Country) + factor(DraftCategory) + YIM + WeightPounds + TOI + factor(DraftCategory):factor(Era) + factor(DraftCategory):YIM + factor(Country):factor(Era) + factor(Country):WeightPounds + TOI:Shutouts_y, data = goalies_no_outliers)

summary(bcmodel_goalies)
```

```{r}
bptest(bcmodel_goalies)
shapiro.test(residuals(bcmodel_goalies))
```

```{r}
best.model <- bcmodel_goalies

###### Plot for normality 
ggplot(best.model, aes(x=.fitted, y=.resid)) + geom_point() +geom_smooth() + geom_hline(yintercept = 0)

###### Check Equal Variance Assumption by graphs and the Breusch-Pagan test. If you detect a trend, how would you like to transform the predictors in the model?
bptest(best.model)

###### Shapiro-Wilk normality test also confirms that the residuals are normally distributed if the p-value is larger than the determined alpha value
shapiro.test(residuals(best.model))

ggplot(data=best.model, aes(residuals(best.model))) + geom_histogram(breaks = seq(-4e19,4e19,by=5e18), col="red", fill="blue") + labs(title="Histogram for residuals") + labs(x="residuals", y="Count")

ggplot(best.model, aes(sample=residuals(best.model))) + stat_qq() + stat_qq_line()

```

### Model Prediction test

```{r}
head(goalies_no_outliers, 100)

predict_data = data.frame(Shutouts_y = 7 ,               ## 0 to 13
                            Era = "1"  ,                 ## 1, 2, 3
                            Country = "USA" ,            ## "OTHER" "CAN"   "USA"   "FIN"   "SWE"  
                            DraftCategory = "early" ,    ## "late"   "early"  "middle" NA  
                            YIM = 0 ,                    ## 3  4  1  2 NA  0  7  6  5  8
                            WeightPounds = 210 ,         ## 165 to 238
                            TOI = 3542)                  ## 1012 to 4696


S.V <- predict(bcmodel_goalies, predict_data, interval="predict")      ## Box Cox Model
(S.V * bestlambda_goalie +1 ) ^ {1/bestlambda_goalie}                  ## Box Cox Model Units Converted

predict(goalies.interact.final.no_outliers, predict_data, interval="predict")  ## Interactive Model (no Box Cox) 


##plot(bcmodel_goalies, which=1)

```

## Model prediction distribution visualizations generated from dataset entries

### fits SavePct value to every entry, sorry for the Warning output

```{r}
fit <- list()
output <- list()
for (i in seq_along(goalies_new$SavePct))
{
  predict_data[[i]] <- data.frame(Shutouts_y = goalies_new$Shutouts_y[i],
                            Era = goalies_new$Era[i],
                            Country = goalies_new$Country[i], 
                            DraftCategory = goalies_new$DraftCategory[i], 
                            YIM = goalies_new$YIM[i],                    
                            WeightPounds = goalies_new$WeightPounds[i],         
                            TOI = goalies_new$TOI[i])
  S.V <- predict(bcmodel_goalies, predict_data[[i]], interval="predict")
  S.V <- (S.V * bestlambda_goalie +1 ) ^ {1/bestlambda_goalie}
  goalies_new$SavePct.Calc[i] = S.V
}
```

### visualize distributions

```{r}
favstats(goalies_new$SavePct)
favstats(goalies_new$SavePct.Calc)
ggqqplot(goalies_new$SavePct.Calc, title="Normal Plot of Predicted SavePct", ylab="Predicted SavePct (%)")
ggqqplot(goalies_new$SavePct, title="Normal Plot of Actual SavePct", ylab="Actual SavePct (%)")
```
